### 2021-07-10 src/paper/results/fit.tex
Finish first version of the model fit section.

% rapid test demand

>>>>

% rapid test demand
The most difficult moment to match in our model is the rapid test demand. Since we have
five different channels through which individuals demand rapid tests and many of the
demand curves are at least partially calibrated through survey data. It is therefore very
reassuring that we fit the share of individuals that do weekly rapid tests almost
perfectly. For the share of individuals that have ever done a rapid test our model is
conservative. There are two reasons for this: Firstly, we only introduce rapid tests in
2021. This is due to the small number of rapid tests in 2020 as well as a lack of data on
the number of random tests and who received them. Secondly, there is no randomness in an
individual's rapid test demand. This reduces the randomness in our model at the cost of
having less individuals that only occasionally test themselves. \comment[id=K]{Write that
this makes us underestimate the effect of random tests?} However,
Section~\ref{subsec:model_validation} shows that our results are very robust to changes
in the exact shares of individuals demanding rapid tests.
